mruby Bytecode Loader Using Bluetooth in Multi-VM Environment

### 2016-03-19 EMSOFT2016/diff/0317_thesis.tex
update

%
% File: thesis.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass[conference,compsoc]{IEEEtran}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\small\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    %lineskip=-0.5ex%
}

\title{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
\author{Takuro Yamamoto}
\date{\today}

\begin{document}
\maketitle
\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
mruby application bytecode modified frequently is sent from a host to a target device by developers.
mruby library bytecode modified infrequently is preserved beforehand with the platform in a storage/ROM device at the time of the first compilation.
In addition, multiple mruby programs cooperatively run in the proposed framework.
A RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
Synchronization of starting multiple tasks is also implemented with Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}
\section{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

@@

%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM sceduler.
mruby on TECS has several problems at present.
One of the problems is low software development efficiency.
mruby on TECS only supports a storage/ROM device in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
For example, an SD card should be inserted and pulled out repeatedly, or a ROM should be rewritten if mruby programs are modified.
Developers should also restart an OS on a target device.
%Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks do not run unless developers call the OS's function.
%In addition developers must prepare as many VMs as the number of tasks because one RiteVM supports only one task.
Moreover, although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
These problem are a big burden on developers.

This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a strage device only once at the beginning and to transfer mruby application codes from a host to a target device.
The RiteVM scheduler enables developers to run multitasking programs more easily than mruby on TECS.
%Specifically, a periodic handler of switching tasks is implemented.
%This paper evaluates the proposed framework in term of data transfer rate, overhead of periodic handler and execution time.

{\bf Contribution}: The proposed framework gives the contribution in the following points.
\begin{enumerate}
\item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
The loader supports the countinuous loading, which saves the Bluetooth set-up time.
Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
In addition, synchronization of multiple tasks is also implemented.
\item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
\end{enumerate}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/proposed.pdf}
    \caption{System Model}
    \label{fig:proposed}
\end{figure}

@@

Ruby is a object-oriented script language \cite{url:Ruby}.
As the main feature, Ruby is easy-to-use and easy-to-read due to its simple grammar.
Ruby can run a program with fewer code lines than C language.
Ruby improves the productivity of a software development owing to not only simple grammar also object-oriented functions such as classes and methods, exceptions, and garbage collection.

mruby is suitable for embedded systems because of faster execution with less amount of resources and takes over the usability and readability of Ruby.
In addition, VM (Virtual Machine) mechanism is used in mruby, therefore mruby programs can run on any operating system as long as VM is implemented.
A RiteVM is a VM in mruby, that runs mruby programs.
The RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which is an intermediate code that can be interpreted by a RiteVM.
The bytecodes can run on a Rite VM, and thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
    \caption{Mechanism of mruby/RiteVM}
    \label{fig:mruby}
\end{figure}

@@

\subsubsection{Component Model}\mbox{}\\

Figure \ref{fig:component} shows a component diagram.
A {\it cell} which is an instance of a component in TECS consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
A {\it entry} port is an interface to provide functions with other {\it cell}s, and a {\it call} port is an interface to use functions of other {\it cell}s.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
Functions of a {\it cell} are implemented in the C language.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

\subsubsection{Component Description}\mbox{}\\

The description of a component in TECS is divided into three parts, {\it signature}, {\it celltype}, and build description.
TECS code is written in .cdl (component description language) file.
The component description is mentioned with an example shown in Figure \ref{fig:component} as follow.

@@

\subsubsection{System Model}\mbox{}\\

The system model of mruby on TECS is shown in Figure \ref{fig:mrubyontecs}.
Each mruby program, which is bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mrubyontecs.pdf}
    \caption{System Model of existing mruby on TECS}
    \label{fig:mrubyontecs}
\end{figure}

\subsubsection{mruby-TECS Bridge}\mbox{}\\

There is a great difference between the execution time of mruby and C language.
According to  \cite{par:mrubyonTECS}, mruby programs are several hundreds times slower than C programs.
The execution of mruby bytecode on a RiteVM is not as efficient as that of C language.
Thus it is difficult to use mruby for all of code.

@@

Figure \ref{fig:mruby_TECS_bridge} shows an example of use of an mruby-TECS bridge for controlling a motor.
The left side of BridgeMotor belongs to the mruby program.
The right side of BridgeMotor belongs to TECS component.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby_TECS_bridge.pdf}
    \caption{mruby-TECS Bridge}
    \label{fig:mruby_TECS_bridge}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/system_model.pdf}
    \caption{Detailed System Model of the proposed framework}
    \label{fig:system_model}
\end{figure}

@@

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8cm,clip]{figure/bluetooth_loader.pdf}
%     \caption{Development Flow in mruby bytecode loader using Bluetooth}
%     \label{fig:bluetooth_loader}
% \end{figure}

\subsubsection{Component of RiteVM with mruby bytecode loader using Bluetooth} \mbox{}\\

The proposed framework provides a RiteVM with mruby bytecode loader using Bluetooth as TECS component.
The component is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
The component plays a role in receiving bytecodes via Bluetooth, and also manages a RiteVM configuration such as automatically generates the bytecode in the build description.
This generated bytecode is prepared beforehand in the storage/ROM device such as mruby libraries, and different from a bytecode transferred with Bluetooth.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/component_bluetooth.pdf}
    \caption{Component Diagram of mruby bytecode loader using Bluetooth}
    \label{fig:component_bluetooth}
\end{figure}

@@

Finally, the mruby task runs.
When the mruby application is modified, only the bytecode of the modified application should be transferred.
mruby libraries need not be touched because libraries are not normally changed.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/control_flow.pdf}
    \caption{Control Flow of mruby bytecode loader using Bluetooth}
    \label{fig:control_flow}
\end{figure}
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tMrubyBluetooth{
    entry sTaskBody eMrubyBody;
    attr{
      [omit]char_t *mrubyFile;
      char_t *irep = C_EXP("&$cell_global$_irep");
      uint32_t irepAppSize = C_EXP( BUFFER_SIZE );
    };
    var{
        [size_is(irepAppSize)] uint8_t *irepApp;
    };
};
\end{lstlisting}
\caption{Celltype Description for RiteVM with mruby bytecode loader using Bluetooth}
\label{celltype_mrubybluetooth}
\end{figure}
\begin{figure}[t]
\centering
\begin{lstlisting}
void
eMrubyBody_main( CELLIDX idx )
{
  /* Declaration variables */
  mrb_state *mrb;
  mrbc_context *c;
  /* New interpreter instance */
  mrb = mrb_open();
  // Omit: error check for mrb_state
  /* New mruby context */
  c = mrbc_context_new( mrb );
  // Omit: initialization of mruby-TECS bridge
  /* Receive the bytecode via Bluetooth */
  bluetooth_loader( VAR_irepApp );
  /* Load mruby library bytecode and run */
  mrb_load_irep_cxt( mrb, ATTR_irep, c );
  /* Load mruby application bytecode and run */
  mrb_load_irep_cxt( mrb, VAR_irepApp, c );
  if ( mrb->exc ) {
    /* Failure to execute */
    mrb_p( mrb, mrb_obj_value( mrb->exc ) );
    exit( 0 );
  }
  /* Free mruby context */
  mrbc_context_free( mrb, c );
  /* Free interpreter instance */
  mrb_close( mrb );
}

@@

\subsubsection{RiteVM Scheduler} \mbox{}\\

A RiteVM scheduler is a periodic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
The design of the RiteVM scheduler is shown in Figure \ref{fig:rotateReadyQueue}. 
{\it rotateReadyQueue} is described as follows.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/rotateReadyQueue.pdf}
    \caption{The design of RiteVM sceduler}
    \label{fig:rotateReadyQueue}
\end{figure}

\subsubsection{Component of RiteVM Scheduler} \mbox{}\\

Figure \ref{fig:cyclic_handler} shows a component diagram of the periodic handler.
The components of periodic handler consist of two components: CyclicHandler and CyclicMain.
CyclicHandler {\it cell} configures the periodic handler based on $\mu$ITRON.
Cyclic handlers based on $\mu$ITRON are described in detail \cite{par:microITRON}.
The periodic handler has five arguments: ID, attribute, periodic time, periodic phase and access pattern.
CyclicHandler {\it cell} has these arguments as attributes of the {\it cell}.
CyclicMain {\it cell} is a component to perform the processing body of a periodic handler.
{\it rotateReadyQueue} is implemented as the body.
Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port, an {\it entry} port and an attribute.
The {\it call} port is connected with the {\it entry} port of the Kernel {\it cell} ({\it tkernel.eiKernel}) to call functions of the kernel. 
The attribute is used as an arguments of {\it rotateReadyQueue}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/cyclic_handler.pdf}
    \caption{Component Diagram of Cyclic Handler}
    \label{fig:cyclic_handler}
\end{figure}
\begin{figure}[t]
    \centering
    \begin{lstlisting}
celltype tCyclicHandler {
    [inline] entry sCyclic eCyclic;
    call  siHandlerBody  ciBody;
    attr {
    	[omit] ATR    attribute = C_EXP("TA_NULL");
    	[omit] RELTIM cyclicTime;
    	[omit] RELTIM cyclicPhase = 0;
    };
};
celltype tCyclicMain{
    require tKernel.eiKernel;
    entry siHandlerBody eiBody;
    attr {
        PRI priority;
    };
};
    \end{lstlisting}
    \caption{Celltype Description of Cyclic Handler}
    \label{celltype_cyclic_handler}
\end{figure}
\begin{figure}[t]
    \centering
    \begin{lstlisting}
cell tCyclicHandler CyclicHandler{
    ciBody = CyclicMain.eiBody;
    attribute = C_EXP("TA_STA");
    cyclicTime = 1;
    cyclicPhase = 1;
};
cell tCyclicMain CyclicMain{
    priority =
        C_EXP("RITEVM_PRIORITY");
};
   \end{lstlisting}
    \caption{Build Description of Cyclic Handler}
    \label{build_cyclic_handler}
\end{figure}

\subsubsection{Synchronization of Multiple RiteVM Tasks} \mbox{}\\

In the proposed framework, RiteVMs read mruby bytecodes, and then execute the applications.
Eventflag, one of synchronous processing, is applied to synchronize the starting of multiple mruby applications.
Each task sets the flag pattern such as 0x01 (01) and 0x02 (10), and then waits the flag pattern, 0x3 (11), with AND.
This process can also apply to the case of the more tasks.
For example, in the case of the four RiteVM tasks, each task sets the flag pattern such as 0x01 (0001), 0x02 (0010), 0x04 (0100)  and 0x08 (1000), and then waits 0x0f (1111) with AND as shown in Figure \ref{fig:Eventflag} (A).

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/Eventflag.pdf}
    \caption{The design for Eventflag using TECS {\scriptsize *only differences}}
    \label{fig:Eventflag}
\end{figure}

@@

In the framework, RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
Therefore, developers can easily add or remove these components and also reuse them.
For example, if developers do not need the RiteVM scheduler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tRiteVMScheduler.cdl$>$);}.
This advantage of CBD saves developers the labor of rewriting a kernel configuration file.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/comparison_s_c_m.pdf}
    \caption{Comparison of the application execution time with singletask, co-routine, and multitask}
    \label{fig:comparison_s_c_m}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/comparison_msec.pdf}
    \caption{Comparison of the overhead for each cyclic period of calling rotateReadyQueue}
    \label{fig:comparison_msec}
\end{figure}

@@

\begin{table}[t]
    \centering
    \caption{Lines of .c and .cdl file for the number of RiteVM}
    \begin{tabular}{c||cc|c}
                & (A)       & (B)     & Diff  \\ \hline
        .c (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
        .c (Modified)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
        .cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
    \end{tabular}
    \label{tab:codesize}
\end{table}

@@

%%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtranBST2/IEEEtran}
\bibliography{ref}

>>>>

%
% File: thesis.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass{sig-alternate-05-2015}
%\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\small\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    %lineskip=-0.5ex%
}

% Copyright
\setcopyright{acmcopyright}

\title{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
\numberofauthors{3}
\author{
\alignauthor
Takuro Yamamoto\\
    \affaddr{Graduate School of Osaka University}
       % \affaddr{1932 Wallamaloo Lane}\\
       % \affaddr{Wallamaloo, New Zealand}\\
       % \email{trovato@corporation.com}
\alignauthor
Hiroshi Oyama\\
    \affaddr{OKUMA Corporation}
       % \affaddr{P.O. Box 1212}\\
       % \affaddr{Dublin, Ohio 43017-6221}\\
       % \email{webmaster@marysville-ohio.com}
\alignauthor
Takuya Azumi\\
    \affaddr{Graduate School of Osaka University}
       % \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       % \affaddr{Hekla, Iceland}\\
       % \email{larst@affiliation.org}
}
%\author{Takuro Yamamoto}
%\date{\today}

\begin{document}
\maketitle
\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
mruby application bytecode modified frequently is sent from a host to a target device by developers.
mruby library bytecode modified infrequently is preserved beforehand with the platform in a storage/ROM device at the time of the first compilation.
In addition, multiple mruby programs cooperatively run in the proposed framework.
A RiteVM scheduler makes multitasking processing more easy-to-use than that of mruby on TECS.
Synchronization of starting multiple tasks is also implemented with Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}
\section{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

@@

%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM scheduler.
mruby on TECS has several problems at present.
One of the problems is low software development efficiency.
mruby on TECS only supports a storage/ROM device in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
For example, an SD card should be inserted and pulled out repeatedly, or a ROM should be rewritten if mruby programs are modified.
Developers should also restart an OS on a target device.
%Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks do not run unless developers call the OS's function.
%In addition developers must prepare as many VMs as the number of tasks because one RiteVM supports only one task.
Moreover, although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
These problem are a big burden on developers.

This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a storage device only once at the beginning and to transfer mruby application codes from a host to a target device.
The RiteVM scheduler enables developers to run multitasking programs more easily than mruby on TECS.
%Specifically, a periodic handler of switching tasks is implemented.
%This paper evaluates the proposed framework in term of data transfer rate, overhead of periodic handler and execution time.

{\bf Contribution}: The proposed framework gives the contribution in the following points.
\begin{enumerate}
\item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
The loader supports the continuous loading, which saves the Bluetooth set-up time.
Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
In addition, synchronization of multiple tasks is also implemented.
\item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
\end{enumerate}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/proposed.eps}
    \caption{System Model}
    \label{fig:proposed}
\end{figure}

@@

Ruby is a object-oriented script language \cite{url:Ruby}.
As the main feature, Ruby is easy-to-use and easy-to-read due to its simple grammar.
Ruby can run a program with fewer code lines than C language.
Ruby improves the productivity of a software development owing to not only simple grammar but also object-oriented functions such as classes and methods, exceptions, and garbage collection.

mruby is suitable for embedded systems because of faster execution with less amount of resources and takes over the usability and readability of Ruby.
In addition, VM (Virtual Machine) mechanism is used in mruby, therefore mruby programs can run on any operating system as long as VM is implemented.
A RiteVM is a VM in mruby, that runs mruby programs.
The RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which is an intermediate code that can be interpreted by a RiteVM.
The bytecodes can run on a Rite VM, and thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby.eps}
    \caption{Mechanism of mruby/RiteVM}
    \label{fig:mruby}
\end{figure}

@@

\subsubsection{Component Model}
Figure \ref{fig:component} shows a component diagram.
A {\it cell} which is an instance of a component in TECS consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
A {\it entry} port is an interface to provide functions with other {\it cell}s, and a {\it call} port is an interface to use functions of other {\it cell}s.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
Functions of a {\it cell} are implemented in the C language.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/component_diagram.eps}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

\subsubsection{Component Description}
The description of a component in TECS is divided into three parts, {\it signature}, {\it celltype}, and build description.
TECS code is written in .cdl (component description language) file.
The component description is mentioned with an example shown in Figure \ref{fig:component} as follow.

@@

\subsubsection{System Model}
The system model of mruby on TECS is shown in Figure \ref{fig:mrubyontecs}.
Each mruby program, which is bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mrubyontecs.eps}
    \caption{System Model of existing mruby on TECS}
    \label{fig:mrubyontecs}
\end{figure}

\subsubsection{mruby-TECS Bridge}
There is a great difference between the execution time of mruby and C language.
According to  \cite{par:mrubyonTECS}, mruby programs are several hundreds times slower than C programs.
The execution of mruby bytecode on a RiteVM is not as efficient as that of C language.
Thus it is difficult to use mruby for all of code.

@@

Figure \ref{fig:mruby_TECS_bridge} shows an example of use of an mruby-TECS bridge for controlling a motor.
The left side of BridgeMotor belongs to the mruby program.
The right side of BridgeMotor belongs to TECS component.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby_TECS_bridge.eps}
    \caption{mruby-TECS Bridge}
    \label{fig:mruby_TECS_bridge}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/system_model.eps}
    \caption{Detailed System Model of the proposed framework}
    \label{fig:system_model}
\end{figure}

@@

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8cm,clip]{figure/bluetooth_loader.eps}
%     \caption{Development Flow in mruby bytecode loader using Bluetooth}
%     \label{fig:bluetooth_loader}
% \end{figure}

\subsubsection{Component of RiteVM with mruby bytecode loader using Bluetooth}
The proposed framework provides a RiteVM with mruby bytecode loader using Bluetooth as TECS component.
The component is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
The component plays a role in receiving bytecodes via Bluetooth, and also manages a RiteVM configuration such as automatically generates the bytecode in the build description.
This generated bytecode is prepared beforehand in the storage/ROM device such as mruby libraries, and different from a bytecode transferred with Bluetooth.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/component_bluetooth.eps}
    \caption{Component Diagram of mruby bytecode loader using Bluetooth}
    \label{fig:component_bluetooth}
\end{figure}

@@

Finally, the mruby task runs.
When the mruby application is modified, only the bytecode of the modified application should be transferred.
mruby libraries need not be touched because libraries are not normally changed.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/control_flow.eps}
    \caption{Control Flow of mruby bytecode loader using Bluetooth}
    \label{fig:control_flow}
\end{figure}
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tMrubyBluetooth{
    entry sTaskBody eMrubyBody;
    attr{
      [omit]char_t *mrubyFile;
      char_t *irep = C_EXP("&$cell_global$_irep");
      uint32_t irepAppSize = C_EXP( BUFFER_SIZE );
    };
    var{
        [size_is(irepAppSize)] uint8_t *irepApp;
    };
};
\end{lstlisting}
\caption{Celltype Description for RiteVM with mruby bytecode loader using Bluetooth}
\label{celltype_mrubybluetooth}
\end{figure}
\begin{figure}[t]
\centering
\begin{lstlisting}
void
eMrubyBody_main( CELLIDX idx )
{
  /* Declaration variables */
  mrb_state *mrb;
  mrbc_context *c;
  /* New interpreter instance */
  mrb = mrb_open();
  // Omit: error check for mrb_state
  /* New mruby context */
  c = mrbc_context_new( mrb );
  // Omit: initialization of mruby-TECS bridge
  /* Receive the bytecode via Bluetooth */
  bluetooth_loader( VAR_irepApp );
  /* Load mruby library bytecode and run */
  mrb_load_irep_cxt( mrb, ATTR_irep, c );
  /* Load mruby application bytecode and run */
  mrb_load_irep_cxt( mrb, VAR_irepApp, c );
  if ( mrb->exc ) {
    /* Failure to execute */
    mrb_p( mrb, mrb_obj_value( mrb->exc ) );
    exit( 0 );
  }
  /* Free mruby context */
  mrbc_context_free( mrb, c );
  /* Free interpreter instance */
  mrb_close( mrb );
}

@@

\subsubsection{RiteVM Scheduler}
A RiteVM scheduler is a periodic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
The design of the RiteVM scheduler is shown in Figure \ref{fig:rotateReadyQueue}. 
{\it rotateReadyQueue} is described as follows.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/rotateReadyQueue.eps}
    \caption{The design of RiteVM scheduler}
    \label{fig:rotateReadyQueue}
\end{figure}

\subsubsection{Component of RiteVM Scheduler}
Figure \ref{fig:cyclic_handler} shows a component diagram of the periodic handler.
The components of periodic handler consist of two components: CyclicHandler and CyclicMain.
CyclicHandler {\it cell} configures the periodic handler based on $\mu$ITRON.
Cyclic handlers based on $\mu$ITRON are described in detail \cite{par:microITRON}.
The periodic handler has five arguments: ID, attribute, periodic time, periodic phase and access pattern.
CyclicHandler {\it cell} has these arguments as attributes of the {\it cell}.
CyclicMain {\it cell} is a component to perform the processing body of a periodic handler.
{\it rotateReadyQueue} is implemented as the body.
Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port, an {\it entry} port and an attribute.
The {\it call} port is connected with the {\it entry} port of the Kernel {\it cell} ({\it tkernel.eiKernel}) to call functions of the kernel. 
The attribute is used as an arguments of {\it rotateReadyQueue}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/cyclic_handler.eps}
    \caption{Component Diagram of Cyclic Handler}
    \label{fig:cyclic_handler}
\end{figure}
\begin{figure}[t]
    \centering
    \begin{lstlisting}
celltype tCyclicHandler {
    [inline] entry sCyclic eCyclic;
    call  siHandlerBody  ciBody;
    attr {
    	[omit] ATR    attribute = C_EXP("TA_NULL");
    	[omit] RELTIM cyclicTime;
    	[omit] RELTIM cyclicPhase = 0;
    };
};
celltype tCyclicMain{
    require tKernel.eiKernel;
    entry siHandlerBody eiBody;
    attr {
        PRI priority;
    };
};
    \end{lstlisting}
    \caption{Celltype Description of Cyclic Handler}
    \label{celltype_cyclic_handler}
\end{figure}
\begin{figure}[t]
    \centering
    \begin{lstlisting}
cell tCyclicHandler CyclicHandler{
    ciBody = CyclicMain.eiBody;
    attribute = C_EXP("TA_STA");
    cyclicTime = 1;
    cyclicPhase = 1;
};
cell tCyclicMain CyclicMain{
    priority =
        C_EXP("RITEVM_PRIORITY");
};
   \end{lstlisting}
    \caption{Build Description of Cyclic Handler}
    \label{build_cyclic_handler}
\end{figure}

\subsubsection{Synchronization of Multiple RiteVM Tasks}
In the proposed framework, RiteVMs read mruby bytecodes, and then execute the applications.
Eventflag, one of synchronous processing, is applied to synchronize the starting of multiple mruby applications.
Each task sets the flag pattern such as 0x01 (01) and 0x02 (10), and then waits the flag pattern, 0x3 (11), with AND.
This process can also apply to the case of the more tasks.
For example, in the case of the four RiteVM tasks, each task sets the flag pattern such as 0x01 (0001), 0x02 (0010), 0x04 (0100)  and 0x08 (1000), and then waits 0x0f (1111) with AND as shown in Figure \ref{fig:Eventflag} (A).

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/Eventflag.eps}
    \caption{The design for Eventflag using TECS {\scriptsize *only differences}}
    \label{fig:Eventflag}
\end{figure}

@@

In the framework, RiteVMs, the RiteVM scheduler, and Eventflag are implemented as components.
Therefore, developers can easily add or remove these components and also reuse them.
For example, if developers do not need the RiteVM scheduler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tRiteVMScheduler.cdl$>$);}.
This advantage of CBD saves developers the labor of rewriting a kernel configuration file.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/comparison_s_c_m.eps}
    \caption{Comparison of the application execution time with singletask, co-routine, and multitask}
    \label{fig:comparison_s_c_m}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/comparison_msec.eps}
    \caption{Comparison of the overhead for each cyclic period of calling rotateReadyQueue}
    \label{fig:comparison_msec}
\end{figure}

@@

\begin{table}[t]
    \centering
    \caption{Lines of .c and .cdl file for the number of RiteVM}
    \begin{tabular}{c||cc|c}
                & (A)       & (B)     & Diff  \\ \hline
        .c (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
        .c (Modification)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
        .cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
    \end{tabular}
    \label{tab:codesize}
\end{table}

@@

%%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{abbrv}
\bibliography{ref}
